Automated Lensing Learner - I: An automated Strong Lensing Identification Pipeline

### 2017-03-09 ms.tex
Added first two paragraphs to discussion

The first step of our pipeline consists of a feature extraction stage,
where our feature vector is a {\em histogram of oriented gradients}
\citep{dalalandtriggs_05} that quantifies edges in the image.  We
describe the method and parameter search in Section~\ref{sec:hog}.  We
then use {\em Logistic Regression} (LR), a machine learning algorithm
described in Section~\ref{sec:LR}, to train a classifier model on a
subset of our images.  LR requires a parameter search over the
regression coefficient, $C_{LogReg}$, which we explore in
Section~\ref{sec:regularization}.  We briefly comment that tests with
\todo{{\em Support Vector Machine} (SVM) as an alternative machine
  learning algorithm yielded negligible performance improvement, and
  increased computation cost.  We do not include SVM in our final
  analysis and comparisons.}

@@

Finally, the resolution of the overall image will also limit the
additional information that an increase in $N_\text{orient}$ will
provide.  \wording{For the LSST-like data, the optimal orientation is
  $N_\text{orient}=?$ compared with $N_\text{orient}=?$ only results
  in a $???\%$ improvement.}

% Impact on image performance
The image size affects the length of the HOG feature vector, which has
a monotonically increasing relationship with the time required to
train the model.  Additionally, for fixed memory restrictions, there
is a tradeoff between the length of the feature vector and the size of
the training set.  We will discuss how the training set size affects
the train time for each data set in Section~\ref{sec:trainsetsize}.

@@

% Train time behavior for nLSST10
Since nLSST10 does not contain the lens galaxies, fewer of the
extracted features describe the lensing system, requiring decreased
model complexity.  The increase in train time for nLSST10 as a
function of train size is mostly due to only having more data to fit
in the regression, leading to a steady and slow increase of train time
with number of training images with log-log slope of approximately 1.

@@

%-------------------------------------------------%
\subsection{Image classification performance}\label{sec:performance}
%-------------------------------------------------%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:ROCsamplesLSST10}
\begin{center}
\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/tp.pdf}\hspace{5pt}
\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/fp.pdf}\\\vspace{5pt}
\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/bp.pdf}\hspace{5pt}
\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/bn.pdf}\\\vspace{5pt}
\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/fn.pdf}\hspace{5pt}
\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/tn.pdf}\\
\caption{LSST 10 year mock images. Left two columns: Lens containing
  images, annotated with the image score assigned by our trained
  classifier.  Right two columns: Non-lens containing images,
  annotated with the image score.  The top two rows show
  characteristic images that will be accepted with a high threshold
  for classification, contributing to the bottom left of the ROC curve
  in Figure~\ref{fig:ROCcompilation}.  The middle two rows show
  characteristic images that will be accepted with a moderate
  threshold, contributing to the knee of the ROC curve, with true
  positive rates and false positive rates of $tpr\approx0.8$ and
  $fpr\approx0.2$, respectively.  The bottom two rows show
  characteristic images that will only be accepted with an extremely
  lenient threshold, contributing to the top right area of the ROC
  curve.}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

**Redshift makes sense, but only because of the redshift distribution.
--> Zahid+15 quiescent.... this is where redshifts are from.

% Defining the 6 paradigms of classification
In this section, we discuss the different image types that our model
is most and least able to successfully classify.  We have six
paradigms of model performance on the mock images, \todo{and include a
larger compilation of each of the six image classification paradigms
in the Appendix for the various models we have trained}.

% TP and TN
Figure ~\ref{fig:HSTclassificationtile} shows a tile of representative
HST-like images classified with the model, HST:N5ppc32cpb4C100.  The
left column show lensing systems, and right column non-lensing
systems.  From top to bottom, the images are ordered from highest
scoring to lowest scoring with the classification model.  The top left
is what we would call a ``true positive'', a lensing system that will
always classified as positive because of its high score.  Most of the
highest scoring lensing systems exhibit similar extended arcs
corresponding to a large magnification (see
Section~\ref{sec:peformance_lensmodel}).  The bottom right is a ``true
negative'', a non-lensing system that will likely be classified as
negative because of its low score.  Many of the lowest scoring
non-lensing systems have \todo{fairly small BCGs, which are non likely
  to lens a background galaxy.}

% FN and FP
The bottom left corresponds to a likely ``false negative,'' or a
lensing system that is likely to be mis-classified as a negative.  The
lowest scoring lensing systems tend to have images with smaller
magnification that are minorly distorted, mimicking the shape of
line-of-sight galaxies that the model has learned to ignore.  The top
right corresponds to a likely ``false positive,'' or a non-lensing
system that is likely to be mis-classified as a positive.  False
positives tend to have ``fuzzy'' along the line of sight galaxies that
mimic lensing arcs.  The false positives should be from bright
galaxies along the line of sight.  \todo{The highest scoring
  non-lensing systems often have fairly bright disk shaped galaxies
  along the line of sight.  Visually, these are also virtually
  indistinguishable from a lensed image and would require
  spectroscopic follow-up.}

% BP and BN
The middle row are images whose classification will be most sensitive
to the classification threshold.  We call these borderline images,
with the left corresponding to a ``borderline positive'', and the
right corresponding to a ``borderline negative''.  They sit around the
knee of the ROC curve, the optimal threshold for purity and
completeness.  Note that the ROC curve for HST:N5ppc32cpb4C100
illustrates that we can lower the classification threshold and improve
the true positive rate by $\sim10\%$ and sacrifice an increase in
false positive rate by $\lsim5\%$.  However, small perturbations
around the knee will either include or disinclude the middle row
images.  These are the systems that would make good candidates for
visual and/or spectroscopic follow-up.

%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
%% \begin{figure*}[t]
%%   \centering \mbox{
%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
%%         clip]{figures/HST/1787_lensed_imgs_1.pdf}}\hfill
%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
%%         clip]{figures/HST/1354_unlensed_imgs_1.pdf}} } \mbox{
%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
%%         clip]{figures/HST/1052_lensed_imgs_1.pdf}}\hfill
%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
%%         clip]{figures/HST/1994_unlensed_imgs_1.pdf}} } \mbox{
%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
%%         clip]{figures/HST/1862_lensed_imgs_1.pdf}}\hfill
%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
%%         clip]{figures/HST/1723_unlensed_imgs_1.pdf}} }
%% \caption{HST-like images. The left column corresponds to typical
%%   lensing systems in our sample from highest scoring (top) to lowest
%%   scoring, or false negatives (bottom).  The right column corresponds
%%   to typical non-lensing systems in our sample from highest scoring,
%%   or false positives (top), to lowest scoring (bottom).  The middle
%%   row can be considered ``borderline'' classified images, where the
%%   scores of the lensing and non-lensing system are very close to one
%%   another.  These are systems that will be most sensitive to the
%%   classification threshold.}
%% \label{fig:HSTclassificationtile}
%% \end{figure*}
%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
%% \begin{figure*}[t]
%%   \centering

%% \mbox{
%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
%%         clip]{figures/LSST/BCG/lsst_stack_1204_lensed_imgs_1.pdf}}\hfill
%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
%%         clip]{figures/LSST/BCG/lsst_stack_1534_unlensed_imgs_1.pdf}}
%% }

%% \mbox{
%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
%%         clip]{figures/LSST/BCG/lsst_stack_1384_lensed_imgs_1.pdf}}\hfill
%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
%%         clip]{figures/LSST/BCG/lsst_stack_1703_unlensed_imgs_1.pdf}} 
%% }

%% \mbox{
%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
%%         clip]{figures/LSST/BCG/lsst_stack_1641_lensed_imgs_1.pdf}}\hfill
%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
%%         clip]{figures/LSST/BCG/lsst_stack_1518_unlensed_imgs_1.pdf}} 
%% }

%% \caption{LSST-like images with a BCG. These illustrate the same image
%%   classification paradigms as Figure~\ref{fig:HSTclassificationtile}.
%%   Note, the larger PSF of LSST reduces the resolution of images,
%%   making the arc-like morphology of faint images less significant and
%%   increases the appearance of image-BCG blending.}
%% \label{fig:LSSTBCGclassificationtile}
%% \end{figure*}

%% \begin{figure*}[t]
%%   \centering

%% \mbox{
%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
%%         clip]{figures/LSST/noBCG/lsst_stack_1957_lensed_imgs_0.pdf}}\hfill
%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
%%         clip]{figures/LSST/noBCG/lsst_stack_stamps_1098.pdf}}
%% }

%% \mbox{
%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
%%         clip]{figures/LSST/noBCG/lsst_stack_1634_lensed_imgs_0.pdf}}\hfill
%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
%%         clip]{figures/LSST/noBCG/lsst_stack_stamps_1664.pdf}} 
%% }

%% \mbox{
%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
%%         clip]{figures/LSST/noBCG/lsst_stack_1629_lensed_imgs_0.pdf}}\hfill
%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
%%         clip]{figures/LSST/noBCG/lsst_stack_stamps_1399.pdf}} 
%% }

%% \caption{LSST-like images with no BCG. These illustrate the same image
%%   classification paradigms as Figure~\ref{fig:HSTclassificationtile}.}
%% \label{fig:LSSTnoBCGclassificationtile}
%% \end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
\subsection{Performance dependence on lens-model parameters}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
%-------------------------------------------------%
\subsubsection{Effects of Image Magnification on Scoring}
\label{sec:peformance_lensmodel}
%-------------------------------------------------%

% Summary of subsection
Here, we examine lens-model parameters that affect how well our
pipeline can classify the system.  The lens-model parameters we
examined are the redshift, ellipticity, orientation angle, and
velocity dispersion of the lensing BCG, and also the magnification of
the lensed image compared with its original size.  The magnification
of the lensed image is the most correlated lens-model parameter with
our trained model performance.  The more strongly lensed an image is,
the larger its magnification, and the easier it is for our trained
model to classify.

% Discuss figure
In Figure~\ref{fig:scorevslensparams}, we show the classification
score as a function of image magnification for our HST-like sample.
The left-hand side shows the relation color-coded by the redshift of
the lensing galaxy, and the right-hand side shows the relation
color-coded by the velocity dispersion of the lensing galaxy.  Lensing
systems with images that have magnification $\gsim7$ will almost
certainly be classified as positive with threshold scores above
$\gsim0.5$.  These systems are also those that are most easily
classified by eye.  However, our trained model has varying performance
for systems with lower magnifications.

@@

The relationship between our model performance and these lens
parameters indicates that the magnification of lensed images is the
most relevant, and the distribution of image magnification in a data
set will impact trained model performance.  We did not find
correlations in model performance with other lens parameters.  It is
also useful to keep in mind that lensed galaxy images with
magnification $\lsim5$ (e.g. slightly stretched spherical galaxies)
are often visually indistinguishable from elliptical galaxies along
the line of sight.  \todo{We will discuss how differences between the
  lens-model parameter distributions in the training and test sets
  affect performance in a forthcoming paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]
  \centering

\mbox{
    \subfigure{\includegraphics[width=\columnwidth,trim=0 0 0 0,
        clip]{figures/HST/or5ppc32cpb4/magnitude_d_colorcodedby_z.pdf}}\hfill
    \subfigure{\includegraphics[width=\columnwidth,trim=0 0 0 0,
        clip]{figures/HST/or5ppc32cpb4/magnitude_d_colorcodedby_velocity_dispersion.pdf}}
} 
\caption{Image classification score as a function of lensed image
  magnification.  Left color-coded by redshift, right is color coded
  by the lens velocity_dispersion.}
\label{fig:scorevslensparams}
\end{figure*}

%-------------------------------------------------%
\subsubsection{Performance sensitivity to line-of-sight galaxies}
\label{sec:peformance_lensmodel}
%-------------------------------------------------%

%-------------------------------------------------%
\subsection{Effects of BCG contamination}
%-------------------------------------------------%

Previous works to identify strong lensing systems have often modeled
out the BCG from images to better identify lensed images (???CITE
HERE???).  Here, we test the effects of the BCG by training and
testing models on mock data where the BCG has not been included.  By
construction, these results show the maximal improvement that can be
obtained from BCG subtraction.

Figure~\ref{fig:ROCnobcg} shows the \todo{ROC curve for models of HOG
  feature vectors of mock data with no BCG.  The feature vectors are
  the same HOG parameters as in Figure~\ref{fig:ROC} }.  \todo{The
  grid search over parameter space was similar to that for data with
  the BCG.}

???????

@@

machine learning -> pipeline, and training set.

Future work with training set tests.

@@

\item We have found almost no difference between the Logistic
  Regression and Support Vector Machine algorithms, with Logistic
  Regression performing at a factor of $XX$ faster.  This means that
  features of lens and non-lens images are relatively well separated
  by hyperplanes in feature space.

@@

These results indicate that...

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\section{Sample stacked mock LSST images}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\subsection{BCG included}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

The first step of our pipeline consists of a feature extraction stage,
where our feature vector is a {\em histogram of oriented gradients}
\citep{dalalandtriggs_05} that quantifies edges in the image.  We
describe the method and parameter search in Section~\ref{sec:hog}.  We
then use {\em Logistic Regression} (LR), a machine learning algorithm
described in Section~\ref{sec:LR}, to train a classifier model on a
subset of our images.  LR requires a parameter search over the
regression coefficient, $C_{LogReg}$, which we explore in
Section~\ref{sec:regularization}.  We briefly comment that our initial
tests with {\em Support Vector Machine} (SVM) as an alternative
machine learning algorithm yielded negligible performance improvement,
and significantly increased computation cost.  This indicated that the
features of lens and non-lens images are relatively well separated by
hyperplanes in feature space.  For these reasons, we do not include
SVM in our final analysis and comparisons and continue all discussions
with a linear classifier.

@@

Finally, the resolution of the overall image will also limit the
additional information that an increase in $N_\text{orient}$ will
provide.  The best case number of orientations for each dataset is
$N_\text{orient,HST}=9$, $N_\text{orient,LSST10}=3$, \todo{and
  $N_\text{orient,LSST1}=$.}

% Impact on image performance
The image resolution affects the length of the HOG feature vector,
which has a monotonically increasing relationship with the time
required to train the model.  Additionally, for fixed memory
restrictions, there is a tradeoff between the length of the feature
vector and the size of the training set.  We will discuss how the
training set size affects the train time for each data set in
Section~\ref{sec:trainsetsize}.

@@

% Train time behavior for nLSST10
Since nLSST10 does not contain the lens galaxies, fewer of the
extracted features describe the lens system, requiring decreased model
complexity.  The increase in train time for nLSST10 as a function of
train size is mostly due to only having more data to fit in the
regression, leading to a steady and slow increase of train time with
number of training images with log-log slope of approximately 1.

@@

%-------------------------------------------------%
\subsection{Image Classification Performance}\label{sec:performance}
%-------------------------------------------------%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]
\begin{center}
\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/tp.pdf}\hspace{5pt}
\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/fp.pdf}\\\vspace{5pt}
\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/bp.pdf}\hspace{5pt}
\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/bn.pdf}\\\vspace{5pt}
\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/fn.pdf}\hspace{5pt}
\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/tn.pdf}\\
\caption{LSST 10 year mock images. Left two columns: Lens containing
  images, annotated with the image score assigned by our trained
  classifier.  Right two columns: Non-lens containing images,
  annotated with the image score.  The top two rows show
  characteristic images that will be accepted with a high threshold
  for classification, contributing to the bottom left of the ROC curve
  in Figure~\ref{fig:ROCcompilation}.  The middle two rows show
  characteristic images that will be accepted with a moderate
  threshold, contributing to the knee of the ROC curve, with true
  positive rates and false positive rates of $tpr\approx0.8$ and
  $fpr\approx0.2$, respectively.  The bottom two rows show
  characteristic images that will only be accepted with an extremely
  lenient threshold, contributing to the top right area of the ROC
  curve.}\label{fig:ROCsamplesLSST10}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Populating the ROC Curve}
% Defining the 6 paradigms of classification
In this section, we discuss the different image types that our model
is most and least able to successfully classify.  We have six
paradigms of model performance on the mock images based on the score
an image receives when evaluated by the trained model, and its true
label.  From highest scoring to lowest scoring: True Positives (tp),
False Positives (fp), Borderline Positives (bp), Borderline Negatives
(bn), False Negatives (fn), and True Negatives (tn).

Figure~\ref{fig:ROCsamplesLSST10} illustrates four images from each
paradigm for the holdout test set of LSST10.  The trained model used
the entire 10,000 training set.  The left two columns show lens
systems, and the right two columns show non-lens systems.  The
annotation in the top left corner of each images shows the score,
\todo{and the letters in the bottom right label the paradigm of
  performance.}

% tp, tn description
In general, the true positives (the highest scoring lens systems) have
lensed images with large magnification.  The the true negatives (the
lowest scoring non-lens systems) have small lens galaxies with
galaxies along the line of sight that are rounded.  The successful
classification of these two paradigms are least sensitive to the
threshold.  On the other hand the failed classification of the false
negatives (the highest scoring non-lens systems) and the false
positives (the lowest scoring lens systems) are also least sensitive
to the threshold.  False negatives are typically lens systems with
lensed images of smaller magnification and minor distortions that
mimic along the line of sight galaxies that the model has learned to
ignore.  False positives are often non-lens systems with elongated,
elliptical, or ``fuzzy'', galaxies along the line of sight whose signal
blends with the lens galaxy contributing to the false positive rate
even for conservative thresholds.  Visually, these false positives are
virtually indistinguishable from true arcs, and would require
spectroscopic follow-up.

% Borderlines
The middle two rows of Figure~\ref{fig:ROCsamplesLSST10} illustrate
the borderline positives and borderline negatives. The successful
classification of the borderline positives and negatives are most
sensitive to the threshold, and would be the first candidates for
alternative classification methods, such as visual follow-up.
Thresholds set around these scores yield a true positive rate and
false positive rate of $tpr\approx0.8$ and $fpr\approx0.2$,
respectively.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
\subsubsection{Dependence on Lens-Model Parameters}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Summary of subsection
Here, we examine lens-model parameters that affect how well our
pipeline can classify the system.  The lens-model parameters we
examined are the redshift, ellipticity, orientation angle, and
velocity dispersion of the lensing galaxy, and also the magnification
of the lensed image compared with its original size.  We found that
the magnification of the lensed image is the most correlated
lens-model parameter with our trained model performance, with a
secondary and related correlation with lens galaxy velocity
dispersion.  The more strongly lensed an image is, the larger its
magnification, and the easier it is for our trained model to classify.

% Discuss figure
In Figure~\ref{fig:scorevslensparams}, we show the classification
score as a function of image magnification for lens images in our
HST-like sample.  The left-hand side shows the relation color-coded by
the redshift of the lensing galaxy, and the right-hand side shows the
relation color-coded by the velocity dispersion of the lensing galaxy.
Lensing systems with images that have magnification $\gsim7$ will
almost certainly be classified as positive with threshold scores above
$\gsim0.5$.  These systems are also those that are most easily
classified by eye.  However, our trained model has varying performance
for systems with lower magnifications.

@@

The relationship between our model performance and these lens
parameters indicates that the magnification of lensed images is the
most relevant, and the distribution of image magnification in a data
set will impact trained model performance.  We did not find
correlations in model performance with other lens parameters.  It is
also useful to keep in mind that lensed galaxy images with
magnification $\lsim5$ (e.g. slightly stretched spherical galaxies)
are often visually indistinguishable from elliptical galaxies along
the line of sight.

In a forthcoming paper, we will discuss how class imbalance, or
differences between the lens-model parameter distributions in the
training and test sets affect model performance and will explore a
method to correct for this.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]
  \centering 
  \mbox{
    \subfigure{\includegraphics[width=\columnwidth,trim=0 0 0 0,
        clip]{figures/HST/or5ppc32cpb4/magnitude_d_colorcodedby_z.pdf}}\hfill
    \subfigure{\includegraphics[width=\columnwidth,trim=0 0 0 0,
        clip]{figures/HST/or5ppc32cpb4/magnitude_d_colorcodedby_velocity_dispersion.pdf}}
  } 
\caption{Image classification score on HST mock data as a function of
  lensed image magnification.  Left color-coded by redshift, right is
  color coded by the lens velocity dispersion.}
\label{fig:scorevslensparams}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Summarize paper
We have presented a supervised classification pipeline to
automatically identify galaxy-galaxy strong lensing systems using a
histogram of oriented gradients as a feature extractor, and logistic
regression as a machine learning algorithm.  Our pipeline can easily
be extended to identify other strong lensing features, such as
multiply imaged quasars, and to test alternative features and/or
machine learning algorithms.

% Training set
We have also made use of a new sophisticated set of mock observations,
which will also be made publicly available.  The lensing systems have
lens galaxies generated with a realistic redshift distribution and
along the line of sight galaxies drawn from ultra-deep Hubble
observations.  We have explored results from mock HST, one year LSST,
and ten year LSST observations.

@@

\item We have found almost no difference between the Logistic
  Regression and Support Vector Machine algorithms, with Logistic
  Regression performing at a factor of $XX$ faster.

@@

% Benefits of our method
We emphasize that classical linear classifiers, such as logistic
regression, is scalable and relatively easy to parallelize with open
source tools such as {\em Spark}.  Initial checks indicated that HOG
features are well separated enough for a linear classifier algorithm.
Reproducible results do not require supercomputing resources.

% Impact of work
These results indicate that...

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
%\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
%\section{Sample stacked mock LSST images}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
%\subsection{BCG included}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
